Make any stupid plot you want

### 2021-04-29 draft/sections/intro.tex
contribution sectuib as summary of answers to committee questions

The \textit{continuity} can be described in some datasets by components of the dataset. This is formalized by Munzner's notion of metadata as \textit{keys} into the data structure that return associated \textit{values}\cite{munznerChDataAbstraction}. As shown in \autoref{fig:intro:keys:values}, keys can be labeled indexes, such as the attribute name and row ID, or semantically significant physical entities such as locations on a map. In contrast to Munzner's model, in out model components may describe the keys but are never themselves the keys; instead we propose that keys are points on a topological space encoding the continuity of the data. This allows the metadata to be altered without imposing new semantics on the underlying structure, for example by changing the coordinate systems or time resolution. This value agnostic model also supports encoding datasets where there may be multiple independent variables without having to assume any one variable is inducing the change , for example measures of plant growth given variations in water, sunlight, and time.

For building block library developers, a non-semantic model of data continuity allows for the implementation of components that can traverse data structures without having to know the semantics of the data. Since these building block components are by design \textit{equivariant} and \textit{continuity preserving}, domain specific library developers in different domains that rely on the same continuity, for example 2D continuity, can use the same components to build tools that can make domain specific assumptions. One way we evaluate our model is by reproducing fully constrained domain specific library functionality using our proposed architecture.

\subsection{Contribution}
The contribution of this work is 
\begin{enumerate}
  \item formalization of the topology preserving relationship between data and graphic via continuous maps \autoref{sec:math:graphic:base}
  \item formalization of property preservation from data component to visual representation as monoid action equivariant maps \autoref{sec:math:artist:nu}
  \item functional oriented visualization architecture built on the mathematical model to demonstrate the utility of the model \autoref{sec:math:artist:q}
  \item prototype of the architecture built on Matplotlib's infrastructure to demonstrate the feasibility of the model. \autoref{sec:code:artists}
\end{enumerate}
\end{document}

>>>>

The \textit{continuity} can be described in some datasets by components of the dataset. This is formalized by Munzner's notion of metadata as \textit{keys} into the data structure that return associated \textit{values}\cite{munznerChDataAbstraction}. As shown in \autoref{fig:intro:keys:values}, keys can be labeled indexes, such as the attribute name and row ID, or semantically significant physical entities such as locations on a map. In contrast to Munzner's model, in out model components may describe the keys but are never themselves the keys; instead we propose that keys are points on a topological space encoding the continuity of the data. This allows the metadata to be altered without imposing new semantics on the underlying structure, for example by changing the coordinate systems or time resolution. This value agnostic model also supports encoding datasets where there may be multiple independent variables without having to assume any one variable is inducing the change , for example measures of plant growth given variations in water, sunlight, and time. For building block library developers, a non-semantic model of data continuity allows for the implementation of components that can traverse data structures without having to know the semantics of the data. Since these building block components are by design \textit{equivariant} and \textit{continuity preserving}, domain specific library developers in different domains that rely on the same continuity, for example 2D continuity, can use the same components to build tools that can make domain specific assumptions.

\subsection{Contribution}
In this work, we present a framework for understanding visualization as equivariant continuity preserving maps between topological spaces. Using this mathematical formalism, we develop an architecture specification developers can use to implement components in building block visualization libraries that domain specific library developers can carry through in the tools they build. Our work diverges from previous models of visualization and implementations of those models in that it contributes

\begin{enumerate}
  \item formalization of the topology preserving relationship between data and graphic via continuous maps \autoref{sec:math:graphic:base}
  \item formalization of property preservation from data component to visual representation as equivariant maps \autoref{sec:math:artist:nu}
  \item functional oriented visualization architecture built on the mathematical model to demonstrate the utility of the model \autoref{sec:math:artist:q}
  \item prototype of the architecture built on Matplotlib's infrastructure to demonstrate the feasibility of the model. \autoref{sec:code:artists}
\end{enumerate}
We validate our model by using it to re-design artist and data access layer of Matplotlib, a general purpose visualization tool. We evaluate whether the redesign is successful by comparing it to existing implementation, recreating existing domain specific functionality with the new components, and by implementing components that provide new functionality in Matplotlib. While much of this functionality is currently possible in Matplotlib, a functional approach allows us to implement components in a more robust, modular, reliable way.
\end{document}
